\documentclass{article}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{geometry}

\geometry{margin=1in}

\begin{document}
	
	\setcounter{algorithm}{2}  % Set the algorithm counter to 3 so the next algorithm is numbered 3
	
	\begin{algorithm}
		\caption{\texttt{Facilities\_generator (nb\_locations, seed, min\_demand, max\_demand)}}
		\label{alg:facilities_generator}
		\begin{algorithmic}[1]
			
			\State country\_codes $\gets$ [``EU'', ``CHN'', ``IND'', ``ZAF'', ``USA'', ``TUR'', ``IRN'']
			\State Shapefile $\gets$ ``TM\_WORLD\_BORDERS-0.3.shp''
			\State Boundaries $\gets$ filtered\_locations\_in\_Shapefile
			
			\State Facilities $\gets$ empty\_list
			\State locations $\gets$ empty\_list
			
			\For{each $i$ in country\_codes}
			\State Boundaries.add(Shapefile[i])
			\Comment{Getting country borders.}
			\EndFor
			
			\While{$|\text{locations}| < \text{nb\_locations}$}
			\State location $\gets$ $(U(-180,180), U(-90,90))$
			\If{location is in Boundaries}
			\State locations.add(location)
			\State Boundaries.remove(location)
			\EndIf
			\EndWhile
			
			\For{each $i$ in locations}
			\State TTR[i] $\gets$ $U(2,11)$
			\State SI[i] $\gets$ $U(1,11)$
			\State CAP[i] $\gets$ $U(\text{min\_demand} \times 5, \text{max\_demand} \times 10)$
			\State lon[i] $\gets$ locations[i].longitude
			\State lat[i] $\gets$ locations[i].latitude
			\State Facilities.add(TTR[i], SI[i], CAP[i], lon[i], lat[i])
			\Comment{Assigning facility attributes.}
			\EndFor
			
			\For{each $i$ in facilities}
			\Comment{Haversine distance computation}
			\For{each $j$ in facilities where index[j] < index[i]}
			\State lon1, lat1, lon2, lat2 $\gets$ radians(lon[i], lat[i], lon[j], lat[j])
			\State dlon $\gets$ lon2 - lon1 
			\Comment{Difference in longitude between the two points.}
			\State dlat $\gets$ lat2 - lat1 
			\Comment{Difference in latitude between the two points.}
			\State a $\gets$ sin(dlat / 2)$^2$ + cos(lat1) $\times$ cos(lat2) $\times$ sin(dlon / 2)$^2$
			\Comment{Haversine formula’s component which calculates the square of half the chord length between the points.}
			\State c $\gets$ $2 \times$ atan2($\sqrt{a}$, $\sqrt{1 - a}$) 
			\Comment{Angular distance in radians between the two points on the sphere.}
			\State r $\gets$ 6371 
			\Comment{Radius of Earth in kilometers.}
			\State distance[i][j] $\gets$ r $\times$ c
			\State distance[j][i] $\gets$ distance[i][j]
			\Comment{Distance between facilities.}
			\State TGHG[i][j] $\gets$ distance[i][j] $\times$ 1.05
			\Comment{Multiplied with 1.05 kg/km for trucks. (Source: 8billiontrees)}
			\State TGHG[j][i] $\gets$ TGHG[i][j]
			\EndFor
			\EndFor
			
			\State \Return Facilities
			
		\end{algorithmic}
	\end{algorithm}
	
\end{document}